
\begin{acknowledgments}

I want to express my deepest gratitude to my advisor, Professor Patrick Kastner, for his exceptional guidance, constant support, and mentorship throughout my academic journey and master's thesis. His dedication to excellence and passion for teaching me OpenFOAM has been truly inspiring. Professor Kastner always pushed me to be the best, challenging me to exceed my expectations and strive for excellence in every aspect of my work. 

When I approached Professor Kastner with the idea of pursuing an independent study in OpenFOAM, despite my initial lack of knowledge in the field, he was incredibly encouraging and supportive. Professor Kastner not only motivated me to undertake the project but also provided comprehensive guidance and instruction, patiently teaching me the intricacies of OpenFOAM and equipping me with the necessary skills to succeed.

I am also grateful to Professor Tarek Rakha for his generosity with time and resources. The amount of knowledge and skills I learned from him is extensive. Finally, his commitment to my academic and personal growth has made a significant impact on my journey. Furthermore, I would like to extend my appreciation to Tyrone Marshall my instructor and the co-Director of Energy Lab Perkins\&Will, whose skills have enriched my academic journey in various ways. I would also like to thank Robin Tucker for always being there when in need of assistance. Additionally, I am thankful to my colleagues at the High-Performance Lab for their continual support, sharing of knowledge, and invaluable tips that contributed to my success; Anuradha Kadam, Tarek Sherif, Rawad Elkontar, and Yasser Elmasri.

Lastly, I am deeply thankful to my parents, aunts; Fatoma, May, and Fay, siblings; Hamad, Muneera, Ali, Yousef, and my best friend Noof for their love, encouragement, and understanding throughout this stressful time. Their unconditional support has been my source of strength and motivation.
I am sincerely grateful to each and every one of the individuals who helped me reach this step in my academic work.

\end{acknowledgments}
